Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-27 paper/main.tex
restored deleted shared k diagram

\subsection{Shared Index}
\begin{figure}[!h]
  \centering
  \subfloat[$\dbase_c = \dbase_a \cap \dbase_b$]{\includegraphics[width=.4\columnwidth]{union_k.png}%
  \label{fig:artist:union:k}}
  %\hfill
  \subfloat[$\dbase_c = \varnothing$]{\includegraphics[width=.4\columnwidth]{disjoint_k.png}%
  \label{fig:artist:union:disjoint_k}}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluted  $\dbasepoint \in \dbase_a \cap \dbase_b$}
\end{figure}

@@

\begin{equation}
\label{eq:artist:intersection:basespace}
\begin{tikzcd}
  \dfiber_a \arrow[rrrr, "\vartist_a"] \arrow[rrd, "proj_a" description] &  &             &  & {\Gamma(\gbase_a, \gfiber_a)} \arrow[lld, "ga" description, dashed]  \\
                                                                         &  & \dfiber_{c} &  &                                                                      \\
  \dfiber_b \arrow[rrrr, "\vartist_b"] \arrow[rru, "proj_b" description] &  &             &  & {\Gamma(\gbase_b, \gfiber_b)} \arrow[llu, "g_b" description, dashed]
  \end{tikzcd}
\end{equation}
where the projection functions $i_{\dbase_a},i_{\dbase_b}$ behave such that $i_{\dbase_a}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, $i_{\dbase_b}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, meaning the projection functions yield equivalent points in the disjoint union $\dbase_a \bigsqcup_{\dbase_c} \dbase_b$. Data that is completely disjoint in the index, as shown in \autoref{fig:artist:union:disjoint_k}, is a special case where $\dbase_c=\varnothing$ and therefore there is no constraint on the artist with regards to how this data is rendered.

\paragraph{Shared Fields}

>>>>

\subsubsection{Shared Index}
\begin{figure}[!h]
  \centering
  \subfloat[$\dbase_c = \dbase_a \cap \dbase_b$]{\includegraphics[width=.4\columnwidth]{union_k.png}%
  \label{fig:artist:union:k}}
  %\hfill
  \subfloat[$\dbase_c = \varnothing$]{\includegraphics[width=.4\columnwidth]{disjoint_k.png}%
  \label{fig:artist:union:disjoint_k}}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluted  $\dbasepoint \in \dbase_a \cap \dbase_b$}
\end{figure}

@@

\begin{equation}
\label{eq:artist:intersection:basespace}
\begin{tikzcd}
  \dbase_{c} \arrow[d, "\iota", hook] \arrow[r, "\iota", hook] & \dbase_{b} \arrow[d, "i_{\dbase_b}"]      \\
  \dbase_{a} \arrow[r, "i_{\dbase_a}"]                         & \dbase_{a} \bigsqcup_{\dbase_{c}}\dbase_{b}
  \end{tikzcd}
\end{equation}
where the projection functions $i_{\dbase_a},i_{\dbase_b}$ behave such that $i_{\dbase_a}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, $i_{\dbase_b}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, meaning the projection functions yield equivalent points in the disjoint union $\dbase_a \bigsqcup_{\dbase_c} \dbase_b$. Data that is completely disjoint in the index, as shown in \autoref{fig:artist:union:disjoint_k}, is a special case where $\dbase_c=\varnothing$ and therefore there is no constraint on the artist with regards to how this data is rendered.

\subsubsection{}{Shared Fields}
